---
title: "model-performance-eXtreme-Gradient-Boosting"
author: "Laura Winger"
date: "5/7/2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = normalizePath("../.."))
```

### Load the eXtreme Gradient Boosting model analysis

Load the analysis in the source files of this project which fits all of the random forest models (regression and classification).

```{r echo= FALSE}
library(knitr)
source('./src/4_models/xgboost_model.R')
```



### Examine the eXtreme Gradient Boosting regression model performance for predicting Remaining Useful Life (RUL)

This model is seeking to answer the question: **How many cycles are there (starting now) before the engine will fail?**

```{r echo = FALSE}
library(Metrics)
# determine test root mean square error
rmse <- rmse(test.FD001$ground_truth_rul, tuned_xgb_reg_predictions)

postResample(pred = tuned_xgb_reg_predictions, obs = test.FD001$ground_truth_rul)

#check how many predictions were late
#if negative then late
error <- test.FD001$ground_truth_rul - tuned_xgb_reg_predictions
num_predictions <- length(error)
late <- length(error[error<=-31])
success <- late < 1
```

The root mean square error of this model is `r rmse` cycles. However, there were `r late` predictions (out of `r num_predictions`) for the end of life that were more than 30 cycles after the actual engine failure. This means that the model FPS success is `r success`.



### Examine the eXtreme Gradient Boosting classification model performance for classifying whether or not the engine will fail in the next 30 days

This model is seeking to answer the question: **Will this engine fail in the next 30 cycles?**

```{r echo = FALSE}

# get optimal cut off
library(InformationValue)
optCutOff <- optimalCutoff(test.FD001$class_label, tuned_xgb_class_predictions[,2],optimiseFor = "misclasserror")[1] 

# show confusion matrix
thresh <- optCutOff
out <- factor(ifelse(as.numeric(tuned_xgb_class_predictions[,2]) > thresh, 1, 0), levels = c(0, 1))
caret::confusionMatrix(out, as.factor(test.FD001$class_label), positive = '1')

#check how many failures were missed
sensitivity <- sensitivity(test.FD001$class_label,as.numeric(tuned_xgb_class_predictions[,2]), threshold = optCutOff)
success_class <- sensitivity == 1

```

The confusion matrix for this model with an optimal threshold of `r optCutOff`  is shown. The sensitivity / true positive rate of this model is `r sensitivity`. This means that the model FPS success is `r success_class` because no engine failure can be misclassified (missed).
