---
title: "project-performance"
author: "Laura Winger"
date: "4/19/2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the analysis you want to evaluate from the src directory in the project

Later in the project all funcions for data engineering will be modular and packaged. Additionally, all models will be in functions, so this document will be more modular.

```{r echo= FALSE}
library(knitr)
setwd('./NASA-predictive-maintenance-project')
source('./src/initial_analysis.R')
```

## Examine the model performance

```{r echo = false}
library(Metrics)
# determine test root mean square error
rmse <- rmse(RUL.FD001[1:30,],basic_predictions)

#check how many predictions were late
#if negative then late
error <- RUL.FD001[1:30,]-basic_predictions
num_predictions <- length(error)
late <- length(error<0)
success <- late > 1
```

The root mean square error of the basic model is `rmse` days. However, there were `late` predictions (out of `num_predictions`) for the end of life that were after the engine failure. This means that the model FPS success is `success`.
