---
title: "model-performance-linear"
author: "Laura Winger"
date: "4/19/2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = './NASA-predictive-maintenance-project')
```

### Load the basic linear model analysis

Load the analysis in the source files of this project which fits all of the basic linear models (regression and classification).

```{r echo= FALSE}
library(knitr)
#setwd('./NASA-predictive-maintenance-project')
source('./src/basic_linear_model.R')
```



### Examine the linear model performance for predicting Remaining Useful Life (RUL)

This model is seeking to answer the question: **How many cycles are there (starting now) before the engine will fail?**

```{r echo = FALSE}
library(Metrics)
# determine test root mean square error
rmse <- rmse(test.FD001$ground_truth_rul, basic_linear_predictions)

#check how many predictions were late
#if negative then late
error <- test.FD001$ground_truth_rul - basic_linear_predictions
num_predictions <- length(error)
late <- length(error[error<0])
success <- late < 1
```

The root mean square error of the basic model is `r rmse` days. However, there were `r late` predictions (out of `r num_predictions`) for the end of life that were after the engine failure. This means that the model FPS success is `r success`.



### Examine the logistic model performance for classifying whether or not the engine will fail in the next 30 days

This model is seeking to answer the question: **Will this engine fail in the next 30 cycles?**

```{r echo = FALSE}

# show confusion matrix
#confusionMatrix(basic_logistic_predictions, test.FD001$class_label)

#check how many predictions were late
#if negative then late
misClassError <- mean(ifelse(basic_logistic_predictions > 0.5,1,0) != test.FD001$class_label)
accuracy <- 1-misClassError
success_class <- accuracy == 1
```

The accuracy of this model is `r accuracy`. This means that the model FPS success is `r success_class`.
